{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-10 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

    \textbf{Notations}. 

@@

            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function. 

@@

            Then, we call this function is semi-relative smooth with respect to $A_1$, and semi convex to $A_2$

@@

@@

        \begin{theorem}[affine composite smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}

@@

            Ddenote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$, denote $\Vert A\Vert$ to be the operator norm of the matrix, and $\sigma_{\min}(A)$ to be the smallest non-zero eigenvalues of $A$ in absolute value.

@@

                \frac{\mu}{2}\Vert A(\Pi(x - y) + (1 - \Pi)(x - y))\Vert^2
                \frac{\mu}{2}\Vert A(1 - \Pi)(x - y))\Vert^2
                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (1 - \Pi)(x - y)\Vert^2. 
            These results makes for the final inequalities: 

@@

                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value. 

@@

                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequality: 

@@

                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$. 

@@

    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{m\times n}$ matrices and, $b^{(1)}, b^{(2)}, \ldots, b^{(n)}$ be a list of vectors in $\RR^n$. 
        Suppose $F:\RR^m \rightarrow \overline \RR:= \frac{1}{n}\sum_{i = 1}^{n} F_i(x)$, so it admits representations 
        \begin{align*}
            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)}x - b^{(i)}) + g_i(x)
        \end{align*}
        Where, each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $K^{(i)} > \nu^{(i)} \ge 0, b^{(i)} \in \RR^n$ and $A^{(i)} \in \RR^{m \times n}$. 
        So, each $h_i$ are $\nu^{(i)}$ strongly convex and $K^{(i)}$ Lipschitz smooth. 
        \par
        Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$. 
        $f$ satisifes Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
        \begin{align*}
            f(x) = \sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) = h(\mathcal A x). 
        \end{align*}
    \end{assumption}

@@

        \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 

@@

        \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}

@@

    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\label{lemma:snagp2-one-step-s1-proto}
        Suppose that the sequence $(y_k, x_k, v_k)$ satisfies Definition \ref{def:snapg-v2-aff}. 
        Fix some $k \in \N, k \ge 1$, suppose that $I_k = i$.

@@

        Then for all $\bar x \in \RR^m$, the iterates satisfies the inequality: 

@@

        \todoinline{HERE}

@@

        \begin{align}\label{ineq:snapg2-one-step-stage1-chain1}

@@

        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_p = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_p := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well. 

@@

            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_p

@@

            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p

@@

                \right\Vert^2_p
            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p 

@@

                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_p 

@@

                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p

@@

            \right)\Vert \bar x - x_{k - 1}\Vert^2_p

@@

                \right) \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p

@@

            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_p

@@

            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_p

@@

                \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p

@@

                \Vert \bar x - x_{k - 1}\Vert^2_p 
                + \Vert \bar x - v_{k - 1}\Vert^2_p 
                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p

@@

                \Vert x_{k - 1} - v_{k - 1} \Vert^2_p
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p.

@@

        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-stage1-chain1} it gives: 

@@

                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p

@@

                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p

@@

            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_p 

@@

        For the first inequality, recall that $\Vert \cdot\Vert_p = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$. 
        Now, let's takle the $k = 0$ case. 
        \todoinline{HERE}

@@

>>>>

    \textbf{Notations \textcolor{red}{NEW}}. 
    Unless specifically specified in the context, we use the following notations. 
    $\Pi_C$ denotes the projection onto a set $C$. 
    Let $A \in \RR^{m \times n}$ be a matrix. 
    $\sigma_{\min}(A)$ denotes the smallest non-zero absolute value of all singular values of $A$. 
    Let $\Vert A\Vert$ denotes the spectral norm of the matrix $A$. 
    $I$ denotes the identity operator. 

@@

            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respect to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function. 

@@

            Then, we call this function is $A_1, A_2$ Semi-SCNVX and smooth. 

@@

            With some algebra it can be showned that $A^T_2A_2 \succeq A^T_1A_1$. 

@@

        \begin{theorem}[affine composite with smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}

@@

            Denote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$. 

@@

                \frac{\mu}{2}\Vert A(\Pi(x - y) + (I - \Pi)(x - y))\Vert^2
                \frac{\mu}{2}\Vert A(I - \Pi)(x - y))\Vert^2
                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
            These results Make for the final inequalities: 

@@

@@

                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequalities: 

@@

                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y \ in \RR^{m}$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$. 

@@

    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{m\times n}$ matrices and, $b^{(1)}, b^{(2)}, \ldots, b^{(n)}$ be a list of vectors in $\RR^n$. 
        Suppose $F:\RR^m \rightarrow \overline \RR:= \frac{1}{n}\sum_{i = 1}^{n} F_i(x)$, so it admits representations 
        \begin{align*}
            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)}x - b^{(i)}) + g_i(x)
        \end{align*}
        Where, each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $K^{(i)} > \nu^{(i)} \ge 0, b^{(i)} \in \RR^n$ and $A^{(i)} \in \RR^{m \times n}$. 
        So, each $h_i$ are $\nu^{(i)}$ strongly convex and $K^{(i)}$ Lipschitz smooth. 
        \par
        Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$. 
        $f$ satisfies Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
        \begin{align*}
            f(x) = \sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) = h(\mathcal A x). 
        \end{align*}
    \end{assumption}

@@

        \textbf{Proof of \ref{lemma:iters-snapg2-proto-item1}}. 

@@

        \textbf{proof of \ref{lemma:iters-snapg2-proto-item2}.}

@@

    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\;\label{lemma:snagp2-one-step-s1}\\
        Let the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:snapg-v2-aff}. 
        Fix any $k \in \N \cup\{0\}$, suppose that $I_k = i \in \{1, \ldots, n\}$.

@@

        Then for all $\bar x \in \RR^m, k \ge 1$, the iterates satisfies the inequality: 
        \begin{align}\label{ineq:snagp2-one-step-s1-rslt1}

@@

        \begin{align}\label{ineq:snagp2-one-step-s1-rslt2}
            F(x_0) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2 
            &\le \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2. 

@@

        \begin{align}\label{ineq:snapg2-one-step-s1-chain1}

@@

        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_{\bullet} = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_\bullet := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well. 

@@

            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\bullet

@@

            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

                \right\Vert^2_\bullet
            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 

@@

                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 

@@

                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet

@@

            \right)\Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

                \right) \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet

@@

            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

                \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet

@@

                \Vert \bar x - x_{k - 1}\Vert^2_\bullet 
                + \Vert \bar x - v_{k - 1}\Vert^2_\bullet 
                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet

@@

                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet.

@@

        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-s1-chain1} it gives: 

@@

                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet

@@

                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet

@@

            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_\bullet 

@@

        For the first inequality, recall that $\Vert \cdot\Vert_\bullet = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$. 
        Now, let's tackle the $k = 0$ case. 
        By Definition \ref{def:snapg-v2-aff} it has $\alpha_0 = 1$ and, $v_{- 1} = x_{- 1}$, so that makes $z_0 = \bar x$, and $\tau_0 = 0$ hence, $y_0 = v_{-1} = x_{-1}$. 
        As a consequence it chooses $x_0 = T_{L_k}(y_0 | F_{I_0})$, it means that at the $k = 0$ iteration, the algorithm simplify performs one step of proximal gradient descent at $v_{-1}$ without any momentum. 
        So, we can use Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_0 = \bar x, x^+ = x_0$ and, $B = L_0$: 
            F(x_0) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2 
            \frac{L_0 - \sigma^{(i)}}{2}\Vert \bar x - v_{-1} \Vert^2_\bullet
            + \frac{B}{2}\left\Vert \Pi^{(i)}(\bar x - v_{-1})\right\Vert^2. 
        RHS can be simplified further
            & \frac{L_0 - \sigma^{(i)}}{2}\Vert \bar x - v_{-1} \Vert^2_\bullet
            + \frac{L_0}{2}\left\Vert \Pi^{(i)}(\bar x - v_{-1})\right\Vert^2
            &\le \frac{L_0}{2}\Vert \bar x - v_{-1} \Vert^2_\bullet
            + \frac{L_0}{2}\left\Vert \Pi^{(i)}(\bar x - v_{-1})\right\Vert^2
            & = \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2. 

@@

    From the previous lemma, take note that it's for all $\bar x$. 
    The next lemma discuss some special cases of the previous lemma where some terms of the inequality can be simplified away. 
    \begin{lemma}[SNAPG-V2 one step convergence stage II \textcolor{red}{NEW}]\;\label{snapg2-one-step-s2-proto}\\
        Let the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:snapg-v2-aff}. 
        Fix any $k \in \N \cup\{0\}$, suppose that $I_k = i \in \{1, \ldots, n\}$.
            \item If, each $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, then for all $\bar x \in \RR^m$, $k \ge 1$ it satisfies the inequality: 
            \begin{align}\begin{split}
                + \frac{L_k\alpha_k^2}{2} \left\Vert \bar x - v_k\right\Vert^2
                    \left\Vert v_{k - 1} - \bar x\right\Vert^2
                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
            \end{split}\end{align}
            \item If we choose $\bar x \in \Pi_{\ker A^{(i)}}(y_k)$, then for all $k \ge 1$ it has
    The next lemma adds into the interpolation assumption and take conditional expectations on the inequality. 
